Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-11 paper/main.tex
Update main.tex

\subsection{Open Nighttime Lights}

\subsubsection{Overview}
World Bank Light Every Night is a comprehensive data repository of light satellite images collected at night by 
two sensors for the past 30 years: National Defense Meteorological Satellite Program (DMSP) Line of Business Scanning 
System (OLS), data from 1992 to 2017.Visible infrared imaging radiometer suite (VIIRS) day and night band (DNB) data are 2012-2020.

@@

\subsubsection{Remote sensing}
Research by NASA shows that modern remote sensing technology began with the invention of the camera more than 150 years ago. The 
first original photo appeared as a "still image", but it inspired people's ideas and practices for shooting and looking down on 
the surface of the earth. This idea appeared in the 1840s. The first photos were used for topographic mapping. Later in the First 
World War, the cameras mounted on the aircraft provided a bird's-eye view of a considerable surface area and provided a large amount 
of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached 
a qualitative leap. It is now commonly used to describe the science and art of identifying, observing, and measuring objects without 
directly touching them. The process involves detecting and measuring radiation of different wavelengths reflected or emitted from distant 
objects or materials, through which they can be identified and classified by category/type, substance, and spatial distribution (NASA,2021, August 28).

@@

Polar-orbiting satellites(Fig.~\ref{satellites})are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south.

@@

Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
surface of the earth (NASA,2021, August 28).It is the most commonly used orbit for satellite imaging because it is possible to take 
higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
orbits the earth about 16 times a day (ESA, n.d.).

@@

Very Low Frequency (VLF):ELF is extremely low frequency and extremely low frequency, and its frequency is in the range of 
300 Hz to 30 kHz. It is a kind of radio wave, just like AM/FM signal, but with a lower frequency. It is very useful because 
it is mainly reflected at a height of 60-90 kilometers in the D zone of the earth's ionosphere, so it is effectively guided 
to a global distance in the earth's ionospheric waveguide. It is widely used to set up radio receivers almost anywhere on 
the earth. This signal can receive short radiation from lightning strikes in half of the earth (Stanford VLF Group. n.d.).

Low Frequency (LF):Low frequency refers to the radio frequency (RF) in the range of 30 kHz–300 kHz. Low\-frequency AM 
broadcasting services are widely used in Northern Europe, North Africa, and Asia. In the current era, its main uses are 
aircraft beacons, navigation (LORAN), information, and weather systems. Numerous time signal stations such as MSF, DCF77, 
JJY, and WWVB are located in this frequency band, which is also called the kilometer band or kilometer wave (Low\_frequency,n.d).

Medium Frequency (MF)\:Medium Frequency means radio frequency (RF) in the range of 300 kHz to 3000 kHz. For example, 
the AM broadcast band is a medium wave (MW), and the MF band is also called the 100-meter band, which ranges from 100 
to 1000 hundred meters (Medium\_frequency,n.d).

@@

Very high frequency (VHF) is ITU's electromagnetic wave in the range of 30 to 300 megahertz (MHz), and the corresponding 
wavelength is ten meters to one meter (Wikimedia Foundation. (2021, August 14).

Ultra-high frequency (UHF) is the ITU's 300 megahertz (MHz) and 3 gigahertz (GHz), also known as the decimeter band because 
the wavelength ranges from one meter to one-tenth of a meter. UHF radio waves propagate mainly through the line of sight; 
they can be blocked by various objects, and their transmission capacity will be limited by the blocking of objects. For example, 
TV broadcasting, mobile phones, GPS, WIFI, and walkie-talkies all use UHF to realize the dissemination and communication of data 
information (Wikimedia Foundation. (2021, August 8).

Super High Frequency (SHF):The Super High Frequency (SHF) range is ITU to 3 to 30 gigahertz (GHz). This frequency belongs to 
the microwave band, so radio waves with these frequencies are called microwaves. There are many devices in this frequency range, 
such as radar transmitters, wireless local area networks, satellite communications, and it is also used in industrial microwave 
heating, medical diathermy, and microwave hyperthermia to treat cancer (Wikimedia Foundation,2021, July 15).

Extremely high frequency (EHF) is a radio frequency in the electromagnetic spectrum from 30 to 300 gigahertz (GHz). Its frequency 
is between the ultra-high frequency band and the far-infrared frequency band, and below it is the terahertz frequency band. The 
wavelength of radio waves in this band varies from ten to one millimeter, so it is also called the millimeter-wave band and the 
radiation in its waveband is called millimeter waves (Wikimedia Foundation,2021, August 1).

@@

 Infrared radiation (IR) is a kind of radiant energy and electromagnetic radiation, which is invisible to humans, but we can 
 still feel it. It occurs when atoms absorb and release energy with frequent fluctuations. All objects in the universe emit a 
 certain degree of infrared radiation, such as the sun, fire, and the emergence of thermal imaging technologies are the research 
 results of infrared technology (Lucas, J, 2019, February 27).

@@

 The visible light spectrum is the segment of the electromagnetic spectrum that the human eye can view. Its wavelengths are 
 380 to 700 nanometers.The full spectrum of visible light can be divided into rainbow colors because each color has a different 
 wavelength. Violet has the shortest wavelength, about 380 nanometers, and red has the longest wavelength, about 700 nanometers 
 (NASA, n.d.).

@@

UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X-rays, with a wavelength 
between 400 and 10 nanometers. Among ultraviolet rays, red is the light with the longest wavelength, and violet is the light 
with the shortest wavelength. Therefore, the light with the longest wavelength is called infrared light, and the light with the 
shortest wavelength is called ultraviolet light (Stanford Solar Center, n.d.).

@@

X-rays are a penetrating form of high-energy electromagnetic radiation. The wavelength range of most X-rays is 10 picometers 
to 10 nanometers, the corresponding frequency range is 30 terahertz to 30 hertz (30×1015 Hz to 30×1018 Hz), and the energy range 
is 124 eV to 124 keV (Wikimedia Foundation. (2021, September 1).

@@

In remote sensing, the spatial resolution shows the smallest possible feature that a satellite image can display, which means 
that the size of a pixel on the ground constitutes the smallest "point" of an optical satellite image. If the satellite tries 
to capture the size of the scene 700KM from the earth (300m x 300m), the imaged pixels will be very low and the image will become 
very blurry (Muhebwa, A, nd). The spatial resolution is divided into 3 levels:

@@

Not many details about the capture are determined by the pixels of the spatial resolution. If improvements are made to obtain 
more captured details, a large number of cameras will be required to achieve detailed scenes. For the same purpose, space scientists 
need to use a single-pixel to represent the linear dimension on the ground, where the difference in pixels and colors will be 
recommended for measurements on the earth according to the satellite's use and coding method. In the 1980s, NASA satellite data from 
Landsat had 60 million pixels at the time, but with the advancement of the times and the rapid development of technology, 60 million 
pixels have become less leading. The current highest resolution satellites can provide 30 cm accurate imaging (EARTH OBSERVING SYSTEM,2021, August 2).

@@

The International Commission on Illumination (CIE) organization defines the light response of human vision as the range of 380nm to 
780nm and provides a weight table so that the public can use the instrument to study the measured value at the wavelength multiplied 
by the corresponding human vision (Michael. (2021, June 21)). These tables are provided at intervals of 1 nanometer, 5 nanometers, 
and 10 nanometers. Resolution refers to how many data points are used in the calculation of the image. For the spectral resolution, 
it is to define the measurement point in the spectral result one step further.

@@

Time resolution refers to the repetitive period or frequency at which the sensor revisits the same part of the earth's 
surface. Think of it as the time to take multiple measurements of the cross-section and then reconstruct the image. This 
time is also called the "revisit time" of the satellite. For example, the greater the stripe width of a polar-orbiting 
satellite, it is regarded as the width of the sensor's "cross-orbit" field of view during the passage of the orbit, and 
the higher the resolution time (Watson, N. J, 2015).

@@

The Resources on AWS:

@@

This picture is showing lots of folders of nighttime data.  In those folders, there are tons of.OIS files. 
For example: F12199501010014.night.OIS

F12 \-\> satellite name \\
1995 \-\> year at start of orbital segment \\
01 \-\> month at start of orbital segment \\
01 \-\> day of month at start of orbital segment \\
00 \-\> hour of day at start of orbital segment \\
14 \-\> minute of hour at start of orbital segment \\
.night \-\> orbit is cropped to only nighttime data \\
.OIS \-\> acronym for OLS Interleaved Smooth \\

@@

The file named npp\_year and month is because of the data collection from VIIRS-DNB (the following DMSP-OLS sensor). 
It has some difference between DMSP.

For example:
SVDNB\_npp\_d20150504\_t1335358\_e1341162\_b18219\_c20150504194116381040\_noaa\_ops.rade9.co.tif

The file structure is:\\
npp\_d20150504\_t1335358\_e1341162\_b18219\\
npp:satellite ID\\
d20150504: start date of first scan in aggregate (2015/05/04)\\
t1335358: time of first scan (13:35:35.8)\\
e1341162: time of last scan (13:41:16.2)\\
b18219: orbit number of first scan\\

SVDNB\_npp\_d20150504\_t1335358\_e1341162\_b18219\_c20150504194116381040\_noaa\_ops\\
SVDNB: Day/Night Band SDR (all possible product IDs are listed below)\\
npp\_d20150504\_t1335358\_e1341162\_b18219: aggregate identifier\\
C20150504194116381040: creation date/time of SDR\\
noaa:data origin\\
ops:data domain

@@

In GIS, raster data is usually used as the background display screen of other feature layers. Such layers are orthophotos, 
which not only provide additional information but also make map users more confident that the map layers are spatially 
aligned and represent actual objects. There are three main sources of such images, namely orthophoto aerial photography, 
orthophoto satellite images, and orthophoto scanned maps (ArcGIS for Desktop, (n.d.).

@@

Rasters are usually used to represent data that changes continuously along the surface, such as rainfall, temperature, 
density, etc. The map draws the surface of the map through the continuously changing data of countless small grids. The 
continuous change of grid color reflects the change of a region at present or within a period (ArcGIS for Desktop, (n.d.).

@@

In our project, the vector format data is not the main research object, but it is also a format that our team needs 
to understand. A vector data file is an image that can be scaled to any size without losing its quality and clarity. 
Changing the file has an advantage because its scaling depends on mathematical equations. This vector file is more 
flexible and has perfect image quality. Compared with Raster files, pixilation will not lose sharpness when zooming 
in, and raster graphics will be greatly affected to form sharp contrasts (Logogenie.net,n.d.).

@@

Cloud Optimization GeoTIFFs (COG) is a cloud-optimized file viewing, reading, and usage solution. The OGC GeoTIFF standard 
is the OGC implementation standard (NASA, 2021, September 8). The files of GeoTIFFs are also GeoTIFF, and this data structured 
method allows users to query these files through Web services. However, this advantage allows users to query, analyze, visualize 
or download part of the COG file online without downloading the entire file. Such a database reading solution is also used by our team.

@@

The SpatioTemporal Asset Catalog (STAC) specification provides a common language to describe a series of geospatial 
information in order to provide easier indexing and searching. A "space-time asset" is any file that represents information 
about the Earth captured in a specific space and time. The STAC specification is to allow all providers to publish new data 
sets or APIs without writing new code when they are published as a spatiotemporal asset catalog (SpatioTemporal Asset Catalog, n.d.). 
First of all, for providers, STAC is a standardized method for exposing Spatio-temporal data collections while cataloging 
assets and STAC is also a unified asset indexing method. Second, developers can build infrastructure to host, ingest, or 
manage spatial data collections, and can be extended to customize domains. Finally, data consumers often have to build a 
unique pipeline for each different data set they use.

@@

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quit the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank---Light Every Light doucument,and I have done further study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
    Writing part:
    I have wrote the Light Every night part of paper in solution summary. And in proposed solution,I have wrote part of process the data.

>>>>

	\subsubsection{Overview}
	World Bank---Light Every Night\cite{WorldBan13:online} is a comprehensive data repository of light satellite images collected at night by 
	two sensors for the past 30 years: National Defense Meteorological Satellite Program (DMSP) Line of Business Scanning 
	System (OLS), data from 1992 to 2017.Visible infrared imaging radiometer suite (VIIRS) day and night band (DNB) data are 2012-2020.

@@

	\subsubsection{Remote sensing}
	Research by NASA shows that modern remote sensing technology began with the invention of the camera more than 150 years ago. The 
	first original photo appeared as a "still image", but it inspired people's ideas and practices for shooting and looking down on 
	the surface of the earth. This idea appeared in the 1840s. The first photos were used for topographic mapping. Later in the First 
	World War, the cameras mounted on the aircraft provided a bird's-eye view of a considerable surface area and provided a large amount 
	of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached 
	a qualitative leap. It is now commonly used to describe the science and art of identifying, observing, and measuring objects without 
	directly touching them. The process involves detecting and measuring radiation of different wavelengths reflected or emitted from distant 
	objects or materials, through which they can be identified and classified by category/type, substance, and spatial distribution\cite{earthdata28:online}.

@@

	Polar-orbiting satellites(Fig.~\ref{satellites})are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
	plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
	to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
	the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
	moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south..

@@

	Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
	2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
	surface of the earth (NASA,2021, August 28).It is the most commonly used orbit for satellite imaging because it is possible to take 
	higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
	for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
	second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
	orbits the earth about 16 times a day\cite{ESAkerne12:online}.

@@

	Very Low Frequency (VLF):ELF is extremely low frequency and extremely low frequency, and its frequency is in the range of 
	300 Hz to 30 kHz. It is a kind of radio wave, just like AM/FM signal, but with a lower frequency. It is very useful because 
	it is mainly reflected at a height of 60-90 kilometers in the D zone of the earth's ionosphere, so it is effectively guided 
	to a global distance in the earth's ionospheric waveguide. It is widely used to set up radio receivers almost anywhere on 
	the earth\cite{Introduc19:online}. This signal can receive short radiation from lightning strikes in half of the earth.

	Low Frequency (LF):Low frequency refers to the radio frequency (RF) in the range of 30 kHz–300 kHz. Low\-frequency AM 
	broadcasting services are widely used in Northern Europe, North Africa, and Asia. In the current era, its main uses are 
	aircraft beacons, navigation (LORAN), information, and weather systems. Numerous time signal stations such as MSF, DCF77, 
	JJY, and WWVB are located in this frequency band, which is also called the kilometer band or kilometer wave\cite{httpswww63:online}.

	Medium Frequency (MF)\:Medium Frequency means radio frequency (RF) in the range of 300 kHz to 3000 kHz. For example, 
	the AM broadcast band is a medium wave (MW), and the MF band is also called the 100-meter band, which ranges from 100 
	to 1000 hundred meters\cite{httpswww49:online}.

@@

	Very high frequency (VHF) is ITU's electromagnetic wave in the range of 30 to 300 megahertz (MHz), and the corresponding 
	wavelength is ten meters to one meter (Wikimedia Foundation\cite{Veryhigh48:online}.

	Ultra-high frequency (UHF) is the ITU's 300 megahertz (MHz) and 3 gigahertz (GHz), also known as the decimeter band because 
	the wavelength ranges from one meter to one-tenth of a meter. UHF radio waves propagate mainly through the line of sight; 
	they can be blocked by various objects, and their transmission capacity will be limited by the blocking of objects. For example, 
	TV broadcasting, mobile phones, GPS, WIFI, and walkie-talkies all use UHF to realize the dissemination and communication of data 
	information (Wikimedia Foundation\cite{Ultrahig37:online}.

	Super High Frequency (SHF):The Super High Frequency (SHF) range is ITU to 3 to 30 gigahertz (GHz). This frequency belongs to 
	the microwave band, so radio waves with these frequencies are called microwaves. There are many devices in this frequency range, 
	such as radar transmitters, wireless local area networks, satellite communications, and it is also used in industrial microwave 
	heating, medical diathermy, and microwave hyperthermia to treat cancer\cite{Superhig8:online}.

	Extremely high frequency (EHF) is a radio frequency in the electromagnetic spectrum from 30 to 300 gigahertz (GHz). Its frequency 
	is between the ultra-high frequency band and the far-infrared frequency band, and below it is the terahertz frequency band. The 
	wavelength of radio waves in this band varies from ten to one millimeter, so it is also called the millimeter-wave band and the 
	radiation in its waveband is called millimeter waves\cite{Extremel31:online}.

@@

	Infrared radiation (IR) is a kind of radiant energy and electromagnetic radiation, which is invisible to humans, but we can 
	still feel it. It occurs when atoms absorb and release energy with frequent fluctuations. All objects in the universe emit a 
	certain degree of infrared radiation, such as the sun, fire, and the emergence of thermal imaging technologies are the research 
	results of infrared technology\cite{L40416:online}.

@@

	The visible light spectrum is the segment of the electromagnetic spectrum that the human eye can view. Its wavelengths are 
	380 to 700 nanometers.The full spectrum of visible light can be divided into rainbow colors because each color has a different 
	wavelength. Violet has the shortest wavelength, about 380 nanometers, and red has the longest wavelength, about 700 nanometers\cite{Vis73:online}.

@@

	UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X-rays, with a wavelength 
	between 400 and 10 nanometers. Among ultraviolet rays, red is the light with the longest wavelength, and violet is the light 
	with the shortest wavelength. Therefore, the light with the longest wavelength is called infrared light, and the light with the 
	shortest wavelength is called ultraviolet light\cite{uvlight14:online}.

@@

	X-rays are a penetrating form of high-energy electromagnetic radiation. The wavelength range of most X-rays is 10 picometers 
	to 10 nanometers, the corresponding frequency range is 30 terahertz to 30 hertz (30×1015 Hz to 30×1018 Hz), and the energy range 
	is 124 eV to 124 keV (Wikimedia Foundation\cite{XrayWiki61:online}.

@@

	In remote sensing, the spatial resolution shows the smallest possible feature that a satellite image can display, which means 
	that the size of a pixel on the ground constitutes the smallest "point" of an optical satellite image. If the satellite tries 
	to capture the size of the scene 700KM from the earth (300m x 300m), the imaged pixels will be very low and the image will become 
	very blurry\cite{AtlasAIW26:online}. The spatial resolution is divided into 3 levels:

@@

	Not many details about the capture are determined by the pixels of the spatial resolution. If improvements are made to obtain 
	more captured details, a large number of cameras will be required to achieve detailed scenes. For the same purpose, space scientists 
	need to use a single-pixel to represent the linear dimension on the ground, where the difference in pixels and colors will be 
	recommended for measurements on the earth according to the satellite's use and coding method. In the 1980s, NASA satellite data from 
	Landsat had 60 million pixels at the time, but with the advancement of the times and the rapid development of technology, 60 million 
	pixels have become less leading. The current highest resolution satellites can provide 30 cm accurate imaging\cite{Satellit48:online}.

@@

	The International Commission on Illumination (CIE) organization defines the light response of human vision as the range of 380nm to 
	780nm and provides a weight table so that the public can use the instrument to study the measured value at the wavelength multiplied 
	by the corresponding human vision\cite{spectral41:online}. These tables are provided at intervals of 1 nanometer, 5 nanometers, 
	and 10 nanometers. Resolution refers to how many data points are used in the calculation of the image. For the spectral resolution, 
	it is to define the measurement point in the spectral result one step further.

@@

	Time resolution refers to the repetitive period or frequency at which the sensor revisits the same part of the earth's 
	surface. Think of it as the time to take multiple measurements of the cross-section and then reconstruct the image. This 
	time is also called the "revisit time" of the satellite. For example, the greater the stripe width of a polar-orbiting 
	satellite, it is regarded as the width of the sensor's "cross-orbit" field of view during the passage of the orbit, and 
	the higher the resolution time\cite{Topicnot43:online}.

@@

The Resources on AWS\cite{WorldBan13:online}:

@@

	This picture is showing lots of folders of nighttime data.  In those folders, there are tons of.OIS files. 
	\\
	For example: F12199501010014.night.OIS \\
	F12 = satellite name \\
	1995 = year at start of orbital segment \\
	01 = month at start of orbital segment \\
	01 = day of month at start of orbital segment \\
	00 = hour of day at start of orbital segment \\
	14 = minute of hour at start of orbital segment \\
	.night = orbit is cropped to only nighttime data \\
	.OIS = acronym for OLS Interleaved Smooth \\

@@

The file named npp\_year and month is because of the data collection from VIIRS-DNB (the following DMSP-OLS sensor). 
	It has some difference between DMSP.
	\\
	For example:
	SVDNB\_npp\_d20150504\_t1335358\_e13411
	62\_b18219\_c20150504194116381040\_noaa
	\_ops.rade9.co.tif
	The file structure is:\\
	npp\_d20150504\_t1335358\_e1341162\_b18219\\
	npp = satellite ID\\
	d20150504 = start date of first scan in aggregate (2015/05/04)\\
	t1335358 = time of first scan (13:35:35.8)\\
	e1341162 = time of last scan (13:41:16.2)\\
	b18219 = orbit number of first scan
	\\
	The file:SVDNB\_npp\_d20150504\_t1335358\_e1341162\_
	b18219\_c20150504194116381040\_noaa\_ops\\
	SVDNB = Day/Night Band SDR (all possible product IDs are listed below)\\
	npp\_d20150504\_t1335358\_e1341162\_b18219 = aggregate identifier\\
	C20150504194116381040 = creation date/time of SDR\\
	noaa = data origin\\
	ops = data domain
	\\

@@

	In GIS, raster data is usually used as the background display screen of other feature layers. Such layers are orthophotos, 
	which not only provide additional information but also make map users more confident that the map layers are spatially 
	aligned and represent actual objects. There are three main sources of such images, namely orthophoto aerial photography, 
	orthophoto satellite images, and orthophoto scanned maps\cite{L什么是栅格数据？15:online}.

@@

	Rasters are usually used to represent data that changes continuously along the surface, such as rainfall, temperature, 
	density, etc. The map draws the surface of the map through the continuously changing data of countless small grids. The 
	continuous change of grid color reflects the change of a region at present or within a period \cite{L什么是栅格数据？15:online}.

@@

	In our project, the vector format data is not the main research object, but it is also a format that our team needs 
	to understand. A vector data file is an image that can be scaled to any size without losing its quality and clarity. 
	Changing the file has an advantage because its scaling depends on mathematical equations. This vector file is more 
	flexible and has perfect image quality. Compared with Raster files, pixilation will not lose sharpness when zooming 
	in, and raster graphics will be greatly affected to form sharp contrasts\cite{Thepaged34:online}.

@@

	Cloud Optimization GeoTIFFs (COG) is a cloud-optimized file viewing, reading, and usage solution. The OGC GeoTIFF standard 
	is the OGC implementation standard\cite{NASA23:online}. The files of GeoTIFFs are also GeoTIFF, and this data structured 
	method allows users to query these files through Web services. However, this advantage allows users to query, analyze, visualize 
	or download part of the COG file online without downloading the entire file. Such a database reading solution is also used by our team.

@@

	The SpatioTemporal Asset Catalog (STAC) specification provides a common language to describe a series of geospatial 
	information in order to provide easier indexing and searching. A "space-time asset" is any file that represents information 
	about the Earth captured in a specific space and time. The STAC specification is to allow all providers to publish new data 
	sets or APIs without writing new code when they are published as a spatiotemporal asset catalog\cite{SpatioTe88:online}. 
	First of all, for providers, STAC is a standardized method for exposing Spatio-temporal data collections while cataloging 
	assets and STAC is also a unified asset indexing method. Second, developers can build infrastructure to host, ingest, or 
	manage spatial data collections, and can be extended to customize domains. Finally, data consumers often have to build a 
	unique pipeline for each different data set they use.

@@

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quit the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank---Light Every Light doucument,and I have done further study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
    Writing part:
   I have wrote the Light Every night part of paper in solution summary. And in proposed solution,I have wrote the process the data.
